Merits of hypermedia systems

### 2013-06-07 dagstuhl-2013/position.tex
Problems with SPARQL
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@589 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

In \cite{kjernsmo_lapis_2012}, examined some practical implications of
the HATEOAS constraint of the REST architectural style, see
\cite{Fielding_2000_Architectural-Styles}~Chapter~5., and in that
light argued why hypermedia RDF is a practical necessity.

@@

Further, we noted that other interesting factors is the
self-description, which is a important characteristic of the RDF
model, and other voiced other minor concerns.

>>>>

Problems with SPARQL interfaces are many: They require extensive
training of developers; it is not immediately clear what data are
available and what may done with the data; it is easy to formulate
queries that will cause the endpoint to become overloaded and hard to
protect against them without also rejecting legitimate queries; it
places heavier systems in the execution path of an application, etc.

@@

In \cite{kjernsmo_lapis_2012}, I examined some practical implications of
the HATEOAS constraint of the REST architectural style, see
\cite{Fielding_2000_Architectural-Styles}~Chapter~5., and in that
light argued why hypermedia RDF is a practical necessity.

@@

Further, we noted that other interesting factors is the
self-description, which is a important characteristic of the RDF
model, and other minor concerns.
